%% ----------------------------------------------------------------
%% Report.tex
%% ---------------------------------------------------------------- 
%TC:macro \inote 1
\documentclass{ecsproject}      % Use the Report Style
\graphicspath{{./Figures/}}   % Location of your graphics files
\usepackage{natbib}            % Use Natbib style for the refs.
\usepackage[nodayofweek]{datetime}
%\usepackage{todonotes}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{color}
\usepackage{booktabs}
\newcommand{\inote}[1] {\todo[inline]{#1}}
\newcommand{\itc}{$I^{2}C$ }
\usepackage[disable]{todonotes}
\usepackage[intoc]{nomencl}
\usepackage{pdfpages}
\removecolourlinks
\makenomenclature
\renewcommand{\nomname}{List of Abbreviations}
%\hypersetup{colorlinks=false}   % Set to false for black/white printing
\input{Definitions}            % Include your abbreviations


%% ----------------------------------------------------------------
\begin{document}
%TC:ignore
\frontmatter
\title      {A Stereoscopic Vision Robot}
\authors    {\texorpdfstring
             {\href{mailto:hl13g10@ecs.soton.ac.uk}{Henry S. Lovett}}
             {Henry S. Lovett}
            }
\department  {Electronics and Computer Science}
\group       {Electronic and Software Systems}
\faculty{Faculty of Physical Sciences and Engineering}
\addresses  {\groupname\\\deptname\\\univname}
\date       {\today}
\subject    {}
\keywords   {}
\supervisor {Prof. Steve Gunn}
\examiner   {Prof. Mark Zwolinski}
\degree     {MEng Electronic Engineering}
\maketitle
\inote{Turn off iNotes!}

\begin{abstract}
\inote{I don't like this. Consider changing...}
This report describes the research, design, build and test of a stereoscopic vision robot using two cameras and an Atmel microcontroller. A custom PCB was designed to fit a wheeled base. 

The report is in two main parts, hardware design and vision algorithms. The hardware design section describes the prototypes and design of the subsystems.
The vision algorithms section discusses range finding from stereo images, comparison algorithms between stereo pairs, and the implementation and test of a two dimensional fast Fourier transform on an AVR. 

The final product is a small mobile robot equipped with cameras and the capability of image processing. The device has the ability to execute a predefined set of commands in an automatic stand-alone way. The robot can also be used as a shell terminal to debug and control.
\end{abstract}

%TC:ignore
\tableofcontents
\listoffigures
\listoftables
\lstlistoflistings
\clearpage
\markboth{\nomname}{\nomname}
\printnomenclature 
\cleardoublepage
\listofsymbols{ll}{
$B$ 					&	Separation distance of two cameras \\
$C_b$					&	$2\pi r_b$ \\
$C_w$					&	Circumference of the wheel \\
$D$						&	Distance from camera to the object \\
$i,j$  					&	Pixel index of an image 	\\
$r_b$					&	Distance from centre of the robot to the wheel \\
$x_0$					&	Horizontal resolution of the image \\
$x_1, x_2$				&	Distance of object from the normal of the camera \\
$\gamma$				&	Number of tabs on the wheel \\
$\Delta_\delta$			&	Distance Resolution \\
$\Delta_\Theta$			&	Rotational Resolution \\
$\delta$				& 	Distance to move \\
$\Theta$				&	Angle of rotation \\
$\sigma$				&	Standard Deviation \\
$\varphi_0$				&	Field of view of the camera \\
$\varphi_1, \varphi_2$	&	Angle from camera to the object \\
}
\nomenclature{CSV}{Comma Separated Value}
\nomenclature{DSP}{Digital Signal Processing}
\nomenclature{EBI}{External Bus Interface}
\nomenclature{USB}{Universal Serial Bus}
\nomenclature{PID}{Proportional Integral Derivative}
\nomenclature{ADC}{Analogue to Digital Converter}
\nomenclature{ASF}{Atmel Software Framework}
\nomenclature{DAC}{Digital to Analogue Converter}
\nomenclature{FFT}{Fast Fourier Transform}
\nomenclature{FIFO}{First In - First Out}
\nomenclature{FPU}{Floating Point Unit}
\nomenclature{GPIO}{General Purpose Input Output}
\nomenclature{ISR}{Interrupt Service Routine}
\nomenclature{I$^2$C}{Inter-Integrated Circuit}
\nomenclature{kB}{Kilobytes}
\nomenclature{NCC}{Normalised Cross Correlation}
\nomenclature{PCB}{Printed Circuit Board}
\nomenclature{PWM}{Pulse Width Modulation}
\nomenclature{SAD}{Sum of Absolute Differences}
\nomenclature{SCCB}{Serial Camera Control Bus}
\nomenclature{SPI}{Serial Peripheral Interface}
\nomenclature{SSD}{Sum of Squared Differences}
\nomenclature{TWI}{Two Wire Interface}
\nomenclature{RISC}{Reduced Instruction Set Computer}
\nomenclature{EEPROM}{Electrically Erasable and Programmable Read Only Memory}
\nomenclature{SRAM}{Static Random-Access Memory}
\nomenclature{SDRAM}{Synchronous Dynamic Random-Access Memory}
\nomenclature{DMIPS}{Dhrystone Million Instructions Per Second}
\nomenclature{USART}{Universal Synchronous/Asynchronous Receiver/Transmitter}
\nomenclature{FAT}{File Allocation Table}
\nomenclature{VSYNC}{Vertical Syncronise}
\nomenclature{WEN}{Write Enable}
\nomenclature{OE}{Output Enable}
\nomenclature{RCLK}{Read Clock}
\nomenclature{HREF}{Horizontal Reference}
\nomenclature{PCLK}{Pixel Clock}
\nomenclature{RRST}{Read Reset}
\nomenclature{WRST}{Write Reset}
\nomenclature{ACK}{Acknowledge}
\nomenclature{NACK}{Negative Acknowledge}


\acknowledgements{I would like to thank Professor Steve Gunn for the weekly meetings no matter where he was in the world, and whose help throughout the year was invaluable. I would also like to thank my friends and family for their support and help throughout my degree and with proof reading, to Tom for our years of being lab partners during our time here, and finally to Alice for asking the two golden questions that solved 90\% of my problems whenever I had one; ``Is it connected?'' and ``Is it switched on?''. }%\\ \\ All work presented in this report is my own unless otherwise stated or referenced. \\ }
\clearpage
\newpage
\authorshipdeclaration{} 
%\dedicatory{To \dots}
%TC:endignore
\mainmatter
%% ----------------------------------------------------------------
\include{Introduction}
\include{Research}
\include{HardwareDevelopment}
\include{InvestigationVision}
%\include{Results}
\include{Conclusions}

\bibliographystyle{ecs}
\addtotoc{References}
\bibliography{ECS}
%TC:ignore
\appendix
\include{Appendix_ProjectBrief}
\include{Appendix_Gantt}
\include{Appendix_CircuitDiagrams}
\include{Appendix_PCB}
\include{Appendix_Costing}
\include{Appendix_TestCode}
\include{Appendix_Contents}
\include{Appendix_Bitmap}
\include{Appendix_RangeDerivations}
%\include{Appendix_Code}
%TC:endignore
\backmatter

\end{document}
%% ----------------------------------------------------------------
